\documentclass{article}

\usepackage{hyperref}

\title{ECE-210-B Syllabus}
\author{Instructor: Jonathan Lam}
\date{Spring 2021}

% don't need special formatting, LaTeX defaults good for me
%\usepackage{titling}
%\pretitle{\begin{center}\huge}
%\posttitle{\end{center}}
%\preauthor{\begin{center}\small}
%\postauthor{\end{center}}
%\predate{\begin{center}\footnotesize}
%\postdate{\end{center}}
%\setlength{\droptitle}{-40pt}

\begin{document}
	\maketitle
	\noindent\textbf{Meeting Time}: Wednesdays, 5-6PM \\
	\textbf{Venue}: MS Teams \\
	\textbf{Contact}: \href{mailto:lam12@cooper.edu}{lam12@cooper.edu} or Teams chat
	
	\subsection*{Course Overview}
	The course material for ECE-210 is a general survey of MATLAB as a programming language, specifically tailored but not limited to its applications in the realm of signals processing. Signals and Systems is a corequisite in the sense that the material from ECE-210 is necessary to perform well in that course, but not the other way around.
	
	This course is 0 credits and your final grade will be Pass or Fail. Nine homeworks will be assigned nearly one each week of the semester. Homeworks are to be submitted by email on Teams as *.m files by 11:59 PM the Wednesday after they are assigned unless otherwise stated.
	
	\subsection*{Grading}
	Each homework assignment will be graded on a scale from 0-3 points dependent on timeliness, completeness, correctness (2 points) and style (1 point). Homeworks may be resubmitted within one week of being returned for full credit. To pass ECE-210, you need only to earn 18 points from the nine homeworks for the semester. Grades on homeworks will be returned within two weeks of submission via Teams.
	
	Attendance is tricky due to online lectures and different time zones. If you are unable to attend lecture, it is okay to only watch the lecture recordings, but please let me know beforehand. Points may be deducted from homework grades for repeated unexcused absences.
	
	Cheating in this course will not be tolerated; any blatant cheating will earn you two zero homework grades, and suspected cheating could earn the class pop quizzes. For everyone's sake, don't! You are better off asking lots of questions or handing in an assignment late than blindly copying from your classmate.
	
	\clearpage
	\subsection*{Contact}
	Any questions regarding the homeworks or lecture may be emailed to me at any time. Questions regarding Signals and Systems may be directed towards myself as well, although they are often better left for Professor Fontaine. If I do not respond to an email in apt time, chances are that I am \textit{not} ignoring you. Please just email me again!
	
	All course materials, including homeworks, lessons and will be uploaded to the Teams channel shortly after the associated lecture. This syllabus is subject to change, but I will try to keep the latest version on Teams and give ample verbal notification of any policy changes should change happen.
\end{document}